Operational Feature Selection with Gaussian Mixture Models for remote sensing images

### 2016-10-13 paper.tex
repetition

\IEEEPARstart{W}{ith} the increasing number of remote sensing missions, the quantity of available data for a given landscape becomes larger and larger. Satellite missions produce a huge amount of data on a regularly (daily) basis. From 2018, the EnMAP (Environmental Mapping and Analysis Program) satellites managed by the German space agency will produce images with 244 spectral bands with a resolution of 30x30m with a frequency of revisit of 4 days\cite{Müller09enmap}. The Hyperspectral Infrared Imager (HyspIRI) of NASA will also deliver images with 212 spectral bands. Additionally to hyperspectral data, the amount of available hypertemporal data increases a lot. For instance, the European satellites Sentinel-2 were launched successfully recently and 2 Terabytes of data will be released every days~\cite{drusch2012sentinel}. This high volume of Earth observation data provides an accurate information of land state and functioning, and help to improve the understanding of the Earth~\cite{rs1010001}. However, processing such data is more and more challenging because of statistical and computational issues.

>>>>

\IEEEPARstart{W}{ith} the increasing number of remote sensing missions, the quantity of available data for a given landscape becomes larger and larger. Satellite missions produce a huge amount of data on a regularly (daily) basis. From 2018, the EnMAP (Environmental Mapping and Analysis Program) satellites managed by the German space agency will produce images with 244 spectral bands with a resolution of 30x30m with a frequency of revisit of 4 days\cite{Müller09enmap}. The Hyperspectral Infrared Imager (HyspIRI) of NASA will also deliver images with 212 spectral bands. Additionally to hyperspectral data, the amount of available hypertemporal data increases a lot. For instance, the European satellites Sentinel-2 were launched successfully recently and 2 Terabytes of data will be released every days~\cite{drusch2012sentinel}. This high volume of Earth observation data provides an accurate information of land state and functioning, and help to improve the understanding of the planet~\cite{rs1010001}. However, processing such data is more and more challenging because of statistical and computational issues.
